The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
fix DT path in manuscript.Rmd

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  bookdown::word_document2:
    reference_docx: template.docx
# bibliography: ../references/knitcite.bib
---

@@

DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
  # bookdown::word_document2:
  #   reference_docx: template.docx
# bibliography: ../references/knitcite.bib
---

@@

DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```
